---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The keywordr SEO package for R

<!-- badges: start -->
<!-- badges: end -->

The *keywordr* package provides an efficient and user-friendly framework for keyword research. The results are typically used to optimize websites for search engines, create content strategy, design information architecture for websites, etc.

## Installation

You can install the development version of keywordr from GitHub with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("MarekProkop/keywordr", build_vignettes = TRUE)
```

Note: You must have [R version 4.1.0](https://www.r-bloggers.com/2021/05/new-features-in-r-4-1-0/) because the package makes use of the native R pipe and the new syntax for anonymous functions.

## Example

This is a basic example which shows you how to use the package:

### Attache packages

```{r libs, message=FALSE}
library(tidyverse)
library(keywordr)
```

### Create a `kwresearch` object and import queries

```{r init}
input_data <- tribble(
  ~query,             ~volume,
  "seo",                96000,
  "seo ye-ji",          22000,
  "seo meaning",         6700,
  "seo services",        6400,
  "what is a seo",       5300,
  "seo london",          5000,
  "what is seo",         4800,
  "seo agency",          4300,
)

kwr <- kwresearch(input_data)
```

### Browse imported queries

```{r}
kwr_queries(kwr)
```

### Prune unwanted queries

```{r}
recipe_file <- file.path(tempdir(), "recipes.yml")

kwr_add_pattern("ye-ji", recipe_file, recipe_type = "remove")

kwr <- kwr |> 
  kwr_prune(recipe_file)
```

### Check pruned queries

```{r}
kwr_queries(kwr)
```

### Explore queries

```{r}
kwr |> kwr_ngrams()
```

### Classify queries

```{r}
kwr_add_pattern(
  pattern = "agenc",
  recipe_file = recipe_file,
  recipe_type = "label",
  dim_name = "bussiness_type",
  value = "agency"
)
kwr_add_pattern(
  pattern = "meaning",
  recipe_file = recipe_file,
  recipe_type = "label",
  dim_name = "info"
)
kwr_add_pattern(
  pattern = "what is",
  recipe_file = recipe_file,
  recipe_type = "label",
  dim_name = "info"
)

kwr <- kwr |> 
  kwr_classify(recipe_file)
```

### Check classified queries

```{r}
kwr_queries(kwr) |> 
  select(1:5)
```

Please see `vignette("workflow")` for a more detailed example.
